---
title: 'Lab week 3: binomial logistic regression'
author: "Ryan Fass"
date: "2023-01-26"
output: html_document
---

```{r setup, echo= TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning= FALSE, message=FALSE)

library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```
Pseudocode:

* Examine the data
* Identify the question
* Wrangle the data
* Identify candidate models
* Select among candidate models using AIC, BIC
* Select among candidate models using k-fold cross validation


```{r}
penguins %>%
  select(species, bill_length_mm:sex) %>%
  GGally::ggpairs(aes(color = species))
```

```{r}
class(penguins$species)
levels(penguins$species)

adelie_chinstrap <- penguins %>% 
  filter(species %in% c('Adelie', 'Chinstrap')) %>% #make sure to use %in% NOT == with filter function
  mutate(species = fct_drop(species)) %>% 
  select(-year) %>% 
  drop_na()

```
## Let's check out the trends across variables

```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~ species)

ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = bill_length_mm)) +
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~ species)
```

## Let's do some binary logistic regression!

```{r}
f1 <- species ~ body_mass_g + flipper_length_mm + sex

ad_chin_blr1 <- glm(formula = f1, data = adelie_chinstrap, #glm= general linear models
                    family = 'binomial') 
ad_chin_blr1
```

Look at the model:
```{r}
ad_chin_blr1
 
summary(ad_chin_blr1)
 
# Get a tidy version w/ broom:
blr1_tidy <- broom::tidy(ad_chin_blr1)
```

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = body_mass_g)) +
  geom_jitter(aes(color = sex))
```

```{r}
blr1_fitted <- ad_chin_blr1 %>% 
  broom::augment(type.predict = 'response')

ggplot(data = blr1_fitted, aes(x = flipper_length_mm, y = .fitted))  +
  geom_point(aes(color = sex, shape = species)) +
 geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper length (mm)",
   	   y = "Probability of outcome Chinstrap")
```


## Predictions for new values with predict()

```{r}
ex1 <- predict(ad_chin_blr1, 
               data.frame(sex = 'female',
                          body_mass_g = 3410, 
                          flipper_length_mm = 192),
               type = 'response')
ex1

new_df <- data.frame(
  sex = c('male', 'female', 'female'),
  body_mass_g = c(3298, 4100, 3600),
  flipper_length_mm = c(212, 175, 180))

ex2 <- predict(ad_chin_blr1, new_df, type = 'response')
ex2
```

## Create a new binary logistic model 

```{r}
f2 <- species ~ bill_length_mm + body_mass_g

ad_chin_blr2 <- glm(formula = f2, data = adelie_chinstrap, family = 'binomial')

ad_chin_blr2
summary(ad_chin_blr2)
blr2_tidy<- broom::tidy(ad_chin_blr2)
```

Let's see if this makes sense based on a visual comparison:
```{r}
ggplot(adelie_chinstrap, aes(x = bill_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species))
```

 ## Model selection
 
```{r}
AICcmodavg::aictab(list(ad_chin_blr1, ad_chin_blr2))

AICcmodavg::bictab(list(ad_chin_blr1, ad_chin_blr2))
```
 
10-fold cross validation

```{r}
set.seed(123)

n_folds <- 10
fold_vec <- rep(1:n_folds, length.out = nrow(adelie_chinstrap))

ad_chin_kfold <- adelie_chinstrap %>% 
  mutate(fold = sample(fold_vec, size =n(), replace = FALSE))
```


purrr::map()
```{r}
x_vec <- 1:10
thing <- purrr::map(.x = x_vec, ### a sequence (vector, list)
                    .f = sqrt) ### a function
thing

my_funct <- function(x, y, z) {
  return((x - y)^z)
}
thing2 <- purrr::map(.x = x_vec, 
                     .f = my_funct,
                     y=2, z = 3)
thing2
```

```{r}
pred_acc <- function(x, y) {
  accurate <- ifelse(x ==y, 1, 0)
  
  return(mean(accurate, na.rm = TRUE))
}

calc_fold <- function(i, fold_df, f) {
  kfold_test <- fold_df %>% 
    filter(fold == i)
  kfold_train <- fold_df %>% 
    filter(fold != i)
  
  kfold_blr <- glm(f, data = kfold_train, family = 'binomial')
  
  kfold_pred <- kfold_test %>% 
    mutate(blr = predict(kfold_blr, kfold_test, type = 'response'),
           pred = ifelse(blr > 0.50, 'Chinstrap', 'Adelie'))
  
  kfold_accuracy <- kfold_pred %>% 
    summarize(blr_acc = pred_acc(species, pred))
  
  return(kfold_accuracy)
}
```


```{r}
results1_purrr_df <- purrr::map(.x = 1:n_folds,
                                .f = calc_fold,
                                fold_df = ad_chin_kfold,
                                f = f1) %>% 
  bind_rows() %>% 
  mutate(md1 = 'f1')

results2_purrr_df <- purrr::map(.x = 1:n_folds,
                                .f = calc_fold,
                                fold_df = ad_chin_kfold,
                                f = f2) %>% 
  bind_rows() %>% 
  mutate(md1 = 'f2')

results_purr_df <- bind_rows(results1_purrr_df, results2_purrr_df) %>% 
  group_by(md1) %>% 
  summarize(mean_acc = mean(blr_acc))
```


# Tidymodels 









